---
title: "Tutorial 4"
author: "Wang Zhe"
output: md_document
---

```{r, message=FALSE, echo=FALSE}
library(ggplot2)
library(dplyr)
```

a)
```{r, message=FALSE, echo=FALSE}
test = matrix(c(3,4,7,2), nrow=2, ncol=2)
colnames(test) <- c("Diabetic Complications-Present","Diabetic Complications-Absent")
rownames(test) <- c("Diabetic Control-Good","Diabetic Control-Poor")
test
prop.table(test,1)
```
The patients who has good diabetic control only 30% of them have diabetic complication present. Those patients who does not have good diabetic control has 66.7% diabetic complication control present.

b)
```{r, message=FALSE, echo=FALSE}
fisher.test(test)
```
The p-value is 0.3024 which is greater than 0.05. Therefore the difference between two groups are not statistically different as it can happen by chance.

c)
The patients are arranged into categories, but it has a very small samples. In addition, it is okay to have some expected counts less than 5, provided none are less than 1, and at least 80% of the expected counts are equal to or greater than 5.